Split `r paste(params$species)` biomass by maturity class

### 2020-11-14 analysis/VOCC/1-split-biomass-by-maturity.Rmd
plot saved maturity ogives

---
title: "Split `r paste(params$species)` biomass by maturity class"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Bocaccio"
    # species: "Threadfin Sculpin"
    #species: "Quillback Rockfish"
    #species: "Yelloweye Rockfish"
    #species: "Shortraker Rockfish"
    # species: "Pacific Ocean Perch"
    region: "All synoptic surveys"
    # region: "Both odd year surveys"
    threshold: 0.5
    split: TRUE
---

@@

#try(biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds")))

@@

>>>>

---
title: "Split `r paste(params$species)` biomass by maturity class"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    # species: "Bocaccio"
    # species: "Redbanded Rockfish"
    species: "Lingcod"
    # species: "Threadfin Sculpin"
    #species: "Quillback Rockfish"
    #species: "Yelloweye Rockfish"
    #species: "Shortraker Rockfish"
    # species: "Pacific Ocean Perch"
    region: "All synoptic surveys"
    # region: "Both odd year surveys"
    threshold: 0.5
    split: TRUE
---

@@

try(biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds")))

@@

From previously saved model
```{r}
savedmodel <- readRDS( file = paste0("data/", spp, 
    "/maturity-ogive-", spp, "-", ssid_string, ".rds"))
(gfranges::plot_mat_ogive(savedmodel) +
        scale_colour_viridis_d(option = "C") +
        ggplot2::ggtitle(paste("Length at maturity for", species)))
ggsave(here::here("ms", "figs", paste0("maturity-", spp, ".png")), width = 4, height = 5)
```
